Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.Rmd
update the language in the introduction

Plotting the residuals against predicted values and each of the explanatory variables on a scatter plot is a recommend way to scrutinize their relationships. If there is any visually discoverable patterns, the model is potentially misspecified. However, correctly judging a residual plot where no pattern exists is a painstakingly difficult task for humans.

It is especially common, particularly among new data analytics students to report patterns when an experienced data analyst might quickly conclude that there are none. [ET: I don't know if the former statement is true? >> PL: change to students] Generally, one looks for noticeable departures from the model like non-linear dependency or heteroskedasticity. It is also possible to conduct hypothesis tests for non-linear dependence [@ramsey_tests_1969], and use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

The persistence of this advice to check the plots is curious, and investigating why this might be common advice is the subject of this paper. The paper is structured as follows. The next background section describes the types of departures that one expects to detect, and describes a formal statistical process for reading residual plots, called visual inference [ET: CITATION HERE? >> PL: arguments removed]. Section \ref{experimental-design} describes the experiment design to compare the decision made by formal hypothesis testing, and how humans would read diagnostic plots. The results are reported in Section \ref{results}. We finish with a discussion on future work, in particular how the responsibility for residual plot reading might be passed on to computer vision.

@@

@@

```{r eval = FALSE}
MASS::glmmPQL(weighted_detect ~ log_effect_size, random = ~ log_effect_size | subject,  family = quasibinomial(), data = vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  mutate(log_effect_size = log10(effect_size)) %>%
  mutate(subject = factor(as.integer(factor(paste(exp, set))))) %>%
  select(log_effect_size, weighted_detect, subject)) -> mod

lme4::glmer(weighted_detect ~ log_effect_size  + (log_effect_size | subject), 
            family = binomial(),
            data = vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
    mutate(log_effect_size = log10(effect_size)) %>%
  mutate(subject = factor(as.integer(factor(paste(exp, set))))) %>%
  select(log_effect_size, weighted_detect, subject)) -> mod

@@

## Data overview

@@

## P-value comparison

@@

@@

>>>>

Residuals might also be plotted, as a scatter plot against the predicted values and each of the explanatory variables to scrutinize their relationships. If there is any visually discoverable patterns, the model is potentially misspecified. However, correctly judging a residual plot where no pattern exists is a painstakingly difficult task for humans. It is especially common, particularly among new data analytics students to report patterns when an experienced data analyst might quickly conclude that there are none. Generally, one looks for noticeable departures from the model like non-linear dependency or heteroskedasticity. It is also possible to conduct hypothesis tests for non-linear dependence [@ramsey_tests_1969], and use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

The persistence of this advice to check the plots is curious, and investigating why this might be common advice is the subject of this paper. The paper is structured as follows. The next background section describes the types of departures that one expects to detect, and describes a formal statistical process for reading residual plots, called visual inference. Section \ref{experimental-design} describes the experiment design to compare the decision made by formal hypothesis testing, and how humans would read diagnostic plots. The results are reported in Section \ref{results}. We finish with a discussion on future work, in particular how the responsibility for residual plot reading might be passed on to computer vision.

@@

# a bit stronger
# plot 7 -> plot 2^3 - 1

@@

```{r eval = FALSE}
MASS::glmmPQL(weighted_detect ~ scale(log_effect_size), random = ~ scale(log_effect_size) | subject,  family = quasibinomial(), data = vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(subject = factor(as.integer(factor(paste(exp, set))))) %>%
  select(log_effect_size, weighted_detect, subject)) -> mod

mod_dat <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  # mutate(log_effect_size = scale(log_effect_size)) %>%
  mutate(subject = factor(as.integer(factor(paste(exp, set))))) %>%
  select(log_effect_size, weighted_detect, subject)

mod <- lme4::glmer(weighted_detect ~ scale(log_effect_size)  + (scale(log_effect_size) | subject), 
                   family = quasibinomial(),
                   data = mod_dat)

mod_dat$log_effect_size

map(seq(-1, 6, 0.1), ~predict(mod, newdata = data.frame(subject = 1:283, log_effect_size = .x), type = "response")) %>%
  `names<-`()

@@

## Overview

@@

## P-value comparison (remove?) (closer to the topic of the paper) (put it after power)

@@

tick mark on x. dashed line too strong. use solid line (grey) in light color.

@@

# invesgating interesting lineups

# change of x_dist -> power

# appendix (contains all the details)

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.tex
update the language in the introduction

Plotting the residuals against predicted values and each of the
explanatory variables on a scatter plot is a recommend way to scrutinize
their relationships. If there is any visually discoverable patterns, the
model is potentially misspecified. However, correctly judging a residual
plot where no pattern exists is a painstakingly difficult task for
humans.

It is especially common, particularly among new data analytics students
to report patterns when an experienced data analyst might quickly
conclude that there are none. {[}ET: I don't know if the former
statement is true? \textgreater\textgreater{} PL: change to students{]}
Generally, one looks for noticeable departures from the model like
non-linear dependency or heteroskedasticity. It is also possible to
conduct hypothesis tests for non-linear dependence
\citep{ramsey_tests_1969}, and use a Breusch-Pagan test
\citep{breusch_simple_1979} for heteroskedasticity.

@@

The persistence of this advice to check the plots is curious, and
investigating why this might be common advice is the subject of this
paper. The paper is structured as follows. The next background section
describes the types of departures that one expects to detect, and
describes a formal statistical process for reading residual plots,
called visual inference {[}ET: CITATION HERE? \textgreater\textgreater{}
PL: arguments removed{]}. Section \ref{experimental-design} describes
the experiment design to compare the decision made by formal hypothesis
testing, and how humans would read diagnostic plots. The results are
reported in Section \ref{results}. We finish with a discussion on future
work, in particular how the responsibility for residual plot reading
might be passed on to computer vision.

@@

@@

\hypertarget{data-overview}{%
\subsection{Data overview}\label{data-overview}}

@@

\hypertarget{p-value-comparison}{%
\subsection{P-value comparison}\label{p-value-comparison}}

@@

>>>>

Residuals might also be plotted, as a scatter plot against the predicted
values and each of the explanatory variables to scrutinize their
relationships. If there is any visually discoverable patterns, the model
is potentially misspecified. However, correctly judging a residual plot
where no pattern exists is a painstakingly difficult task for humans. It
is especially common, particularly among new data analytics students to
report patterns when an experienced data analyst might quickly conclude
that there are none. Generally, one looks for noticeable departures from
the model like non-linear dependency or heteroskedasticity. It is also
possible to conduct hypothesis tests for non-linear dependence
\citep{ramsey_tests_1969}, and use a Breusch-Pagan test
\citep{breusch_simple_1979} for heteroskedasticity.

@@

The persistence of this advice to check the plots is curious, and
investigating why this might be common advice is the subject of this
paper. The paper is structured as follows. The next background section
describes the types of departures that one expects to detect, and
describes a formal statistical process for reading residual plots,
called visual inference. Section \ref{experimental-design} describes the
experiment design to compare the decision made by formal hypothesis
testing, and how humans would read diagnostic plots. The results are
reported in Section \ref{results}. We finish with a discussion on future
work, in particular how the responsibility for residual plot reading
might be passed on to computer vision.

@@

\textbf{test}

@@

\hypertarget{overview}{%
\subsection{Overview}\label{overview}}

@@

\hypertarget{p-value-comparison-remove-closer-to-the-topic-of-the-paper-put-it-after-power}{%
\subsection{P-value comparison (remove?) (closer to the topic of the
paper) (put it after
power)}\label{p-value-comparison-remove-closer-to-the-topic-of-the-paper-put-it-after-power}}

@@

\hypertarget{invesgating-interesting-lineups}{%
\section{invesgating interesting
lineups}\label{invesgating-interesting-lineups}}

\hypertarget{change-of-x_dist---power}{%
\section{change of x\_dist -\textgreater{}
power}\label{change-of-x_dist---power}}
